### 2021-10-05 plos_latex_template.tex
polish rule 8 - Batool

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it should not be a thoughtless default. In the essence of your communication strategy, there should be coherence between actions and words. Always attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team. As you plan the conference, actively reach out and promote the conference to people who have been systematically excluded. Design a promotion plan that reaches communities that are traditionally excluded in scientific meetings. This could be by including representatives from these communities in the organizing team. Always include explicit descriptions of accessibility and other inclusion practices. Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers. Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process. Be careful with the language you use in promoting to the conference and how you talk about minoritized people, Assertively set tone of inclusion.

\begin{itemize}
    \item Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process
    \item Languages
    \item Words matter: Be careful how you talk about minoritized people, Assertively set tone of inclusion
    \item coherence between actions and words
    \item \textbf{networking} when you gather a diverse groups of attendants you also have to take care of the spaces where they will interact
\end{itemize}

If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. Publish the diversity statement (e.g., \url{https://user2021.r-project.org/about/diversity_statement/}), the code of conduct and accessibility guidelines. Fee waivers, financial support, and ease of application/registration should also be advertised; people who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. Advertise the conference in multiple languages (rule \ref{rule_language}). Express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too. 
% Yani: We need to work a little more here, perhaps with some examples.
% Rocío: could add some ideas from here 
% https://www.science.org.au/files/userfiles/support/emcr/documents/one-page-summary-emcr-improving-diversity-web.pdf
% Batool: I will work on this rule to include more details by 25th of Sept

@@

%sara: this fits better in the communication rule
Set the tone. %adding here from Liz's rule but maybe this could go in communication in general
In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being offended.

>>>>

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it should not be a thoughtless default. In the essence of your communication strategy, there should be coherence between actions and words. Always attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team.

As you design the promotion plan, actively reach out and promote the conference to people who have been systematically excluded. If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. This could through publishing the diversity statement (e.g., https://user2021.r-project.org/about/diversitystatement/), the code of conduct and accessibility guidelines, and providing fee waivers and financial support.  People who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. If possible, include representative from these communities within the organizing team (rule \ref{rule_diversity}). Also, try to advertise the conference in multiple languages (rule \ref{rule_language}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

Always include explicit descriptions of accessibility and other inclusion practices (rule \ref{rule_accessibility}). Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers and be public about your commitment to equity and inclusions. Be careful with the language you use in promoting to the conference and how you talk about minoritized people, assertively set tone of inclusion. In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being offended.

Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.

% Yani: We need to work a little more here, perhaps with some examples.
% Rocío: could add some ideas from here 
% https://www.science.org.au/files/userfiles/support/emcr/documents/one-page-summary-emcr-improving-diversity-web.pdf
% Batool: I will work on this rule to include more details by 25th of Sept

@@

%sara: this fits better in the communication rule
%adding here from Liz's rule but maybe this could go in communication in general
%In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being offended.
